Require library
```{r}
# install.packages("jsonlite")
require(jsonlite)
require(stringr)
```

1. Convert the data source format (JSON) to the dataframe. (2M)
```{r}
df <- as.data.frame(fromJSON("Housing2122.json"))
df
```

2. Tidy up the date format to become readable, i.e., 2nd Sep 2021 => 2/9/2021. (8M)
```{r}
df$date <- str_replace_all(df$date, "(st|nd|rd|th)", "")
df$date <- as.Date(df$date, format = "%d %b %Y")
df$date <- format(df$date, "%d/%m/%Y")
df
```

3. Fill all missing data with 0s except the sq. column. (2M)
```{r}
df[, !(names(df) == "sq.")] <- lapply(df[, !(names(df) == "sq.")], function(x) ifelse(is.na(x), 0, x))
df
```

4. Aggregate the number of corresponding facilities (Bed, Baths, Reception). (5M)
```{r}
df[, c("bed", "beds", "bath", "baths", "reception", "receptions")] <- 
  sapply(df[, c("bed", "beds", "bath", "baths", "reception", "receptions")], as.numeric)

df$TotalBeds <- df$bed + df$beds
df$TotalBaths <- df$bath + df$baths
df$TotalReceptions <- df$reception + df$receptions
df <- subset(df, select = -c(bed, beds, bath, baths, reception, receptions))
df
```

5. Extract Property type from “types” column. (10M)
```{r}
df$FlatType <- gsub(" for sale", "", df$types)
df$FlatType <- gsub("^\\d+ bed ", "", df$FlatType)
df$FlatType <- tolower(df$FlatType)
df
```

6. Output your pre-processed data to CSV format called ”Project_Housing.csv”. (3M)
```{r}
write.csv(df, file = "Project_Housing.csv", row.names = FALSE)
```




